Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-10 article/article.tex
mozes
results

Table~\ref{tab:results} illustrates the overall performance of the three classifiers. Rows indicate various feature selection methods. We applied PCA to the original data, while the rest methods were applied to the data belonging to the selected ROIs (cf.~Section~\ref{sec:dimensionalityReduction}). For instance, \emph{Norm/Vox-M-SD ROIs} indicates that we normalised over the voxel values of the same voxel index using the mean and standard deviation, while \emph{Norm-M-SD ROIs} indicates that we normalised over the voxel values of the same scan index using the mean and standard deviation. Columns depict the used classifiers. For the classifiers depicted with *, we used different structure for the data that we fit to them, as described in Section~\ref{}.

From Table~\ref{tab:results} we can distinguish the fact that when PCA is used for feature extraction, the performance of Naive Bayes is lower than when other feature selection methods are used. By using an exact binomial test we found out that the confidence interval of the predictive performance of Naive Bayes when PCA is used is $95\% CI: 56.9 - 65.8$.

We can also distinguish the fact that when different structure is used for the data, the performance increases,

Comparing classifiers when the same structure is used, it is observed that Linear SVM performs better than Naive Bayes. The same remains true when comparing the Multivariate case with Naive Bayes. The former one has better performance.

%mention confidence interval (how much percent sure we are that the actual accuracy of the classifier is between these regions) exact binomial test

>>>>

Table~\ref{tab:results} illustrates the overall performance of the three classifiers. Rows indicate various feature selection methods. We applied PCA to the original data, while the rest methods were applied to the data belonging to the selected ROIs (cf.~Section~\ref{sec:dimensionalityReduction}). For instance, \emph{Norm/Vox-M-SD ROIs} indicates that we normalised over the voxel values of the same voxel index using the mean and standard deviation, while \emph{Norm-M-SD ROIs} indicates that we normalised over the voxel values of the same scan index using the mean and standard deviation. Columns depict the used classifiers. For the classifiers depicted with *, we used different structure for the data, as described in Section~\ref{}.

Furthermore, in order to find out how much percent sure we are that the actually accuracy of the classifiers is between some regions we performed an exact binomial test in each case, from which we obtained the confidence interval. The results were rounded to one decimal point. For the following comparison we are only looking at the case where \emph{Norm/Vox-M-SD ROIs} was used.

From Table~\ref{tab:results} we can distinguish the fact that when PCA is used for feature extraction, the performance of Naive Bayes is lower than when other feature selection methods are used. The confidence interval of the predictive performance of Naive Bayes when PCA is used is 95\% $CI: 56.9 - 65.8$ which suggests that...

Comparing classifiers when the same data structure is used, we can distinguish the fact that Multivariate performs better than Naive Bayes. Also that Linear SVM performs better than Naive Bayes, though not significantly. The confidence interval of Naive Bayes is 95\% $CI: 68.9-77.0$ and of Linear SVM is 95\% $CI: 72.6-80.4$, which suggests that their performances do not differ significantly.

Moreover, when different data structure is used the performance increases, though not significantly. This can be seen by comparing the performance of Naive Bayes when different data structure is used. In the first case it is 73.13\% while in the second case is 76.88\%. The confidence interval in the first case is 95\% $CI: 68.9 - 77.0$ and in the second case is 95\% $CI: 72.8 - 80.6$.

Last but not least, we can distinguish the fact that Multivariate outperforms all the other classifiers, though we did not try a different data structure in the case of Linear SVM. However, we still do not expect that the performance of Linear SVM will be higher that this of Multivariate. The confidence interval of Multivariate is 95\% $CI: 75.7-83.1$.
